Incentivizing Exploration by Heterogeneous Users

### 2018-02-13 algorithm.tex
small edits mostly to the problem setting section, but also to other sections

The algorithm achieving the claimed bounds of
Theorem~\ref{thm:main-overview} is fairly simple.
It mostly allows agents to exploits, but when an arm is estimated to
be extremely unlikely to be pulled by any agents,
the algorithm incentivizes such an arm with a payment that is so high
that the next agent is guaranteed to pull the arm.
This way, the algorithm ensures that each arm is pulled at least a
certain minimum number of times.

>>>>

The algorithm achieving the claimed bounds of
Theorem~\ref{thm:main-overview} is fairly simple.
It mostly allows agents to exploit, but when an arm is \pfdelete{estimated to
be extremely} \pfedit{sufficiently} unlikely to be pulled\pfdelete{by any agents},
the algorithm incentivizes this arm with a payment high enough
to guarantee that the next agent pulls it.
This way, the algorithm ensures that each arm is pulled at least a
certain minimum number of times.

### 2018-02-13 problem_setting.tex
edits to intro
small edits mostly to the problem setting section, but also to other sections

We consider a MAB setting with \ARMNUM arms.
Arm payoffs are determined by $d$ \emph{attributes} or \emph{features};
hence, arms can be identified with vectors $\ArmV{i} \in \R^d$.
The \ArmV{i} are (adversarially) fixed, but unknown to the agents
or the principal.
Whenever arm $i$ is pulled, its current utility-relevant features are
determined as $\ArmV{i} + \NoiseV$, where \NoiseV is a mean-zero
Gaussian%
\footnote{For simplicity of notation, we assume that the variance
  $\sigma^2$ is uniform across time steps. This is not material for
  the analysis.}
noise vector $\NoiseV \sim \Normal{\vc{0}}{\sigma^2 I_{d}}$.
\dkcomment{Clarify if we can handle more general noise.}
Here, $I_d$ denotes the $d \times d$ identity matrix.

At each time $t$, a new user (or \emph{agent}) arrives,
whose feature vector (which we also call his%
\footnote{We use male pronouns to refer to users and female pronouns
  to refer to the principal. 
  \dkcomment{Feel free to switch if you prefer it the other way.}}
\emph{type}) $\AgentV{t} \in \R^d$ is drawn from a known distribution
\AgentDist.
Depending on context, we will identify a agents with their arrival time
$t$ or their type \AgentV{t}.
When agent $t$ pulls arm $\Pull{t} := i$,
he and all future agents observe a vector
$\ObsV{t} = \ArmV{i} + \NoiseV[t]$ for arm $i$,
and his reward is $\AgentV{t} \cdot \ObsV{t}$,
i.e., agents have linear preferences.

@@

Since each user only pulls an arm once, users are \emph{myopic}:
in the absence of incentives, user $t$ will pull an arm from
$\argmax_i \AgentV{t} \cdot \ArmEV{t}{i}$.
To incentivize users to explore more, the principal can offer
\emph{payments} $\Pay{t}{i}$ to user $t$ for pulling arm $i$.
Then, user $t$ will pull an\footnote{We assume that ties are broken in
  favor of an arm with largest payment \Pay{t}{i}; this assumption is
  only for notational convenience, and can of course be avoided by
  raising payments infinitesimally.} arm $i$ maximizing
$\argmax_i (\Pay{t}{i} + \AgentV{t} \cdot \ArmEV{t}{i})$.
The principal cannot observe \AgentV{t},
and only knows the distribution \AgentDist from which it is drawn.
Her goal is to achieve a good tradeoff between the cumulative
\emph{regret} experienced by all users up to time $T$,
and the total \emph{payment} she makes to the users.

@@

To support the formulation of our results and the analysis,
we define the following additional notation.
We let
$\Best{\AgV} \in \argmax_i \AgV \cdot \ArmV{i}$
and
$ \Second{\AgV} \in \argmax_{i \neq \Best{\AgV}} \AgV \cdot \ArmV{i}$
denote the (indices of) the best and second-best arms for an agent
with attribute vector \AgV;
\dkdelete{breaking ties uniformly at random}.
\dkcomment{What would it mean to break ties at random in a
  definition?}

\dkcomment{Do we need this definition here?}
We call time $t_{n}=\min_{t}\{\forall i, N(i,t)\geq n\}$ the
\emph{starting point of the $n^{th}$ round}.
We call the set of times $[t_{n}, t_{n+1})$ the
\emph{$n^{th}$ round}.

@@

Let $\FirstTwo{i}{i'} = \Set{\AgV}{\Best{\AgV} = i, \Second{\AgV} = i'}$
be the set of agent attribute vectors whose best arm is $i$ and
second-best arm is $i'$.
Let $F_{i,i'}$ be the marginal cumulative density function
(or cumulative mass function if $\AgentDist(\cdot)$ is a discrete distribution)
of $(\ArmV{i}-\ArmV{i'}) \cdot \AgV$,
conditioned on $\AgV \in \Omega_{i,j}$.
In words, $F_{i,i'}$ is the distribution of the \emph{strength} of the
preference of a random agent for arm $i$ over arm $i'$, given that
$i$ and $i'$ are the agent's first and second choices.

>>>>

We consider a MAB setting with \ARMNUM arms.
Arm payoffs are determined by $d$ \emph{attributes} or \emph{features};
hence, arms can be identified with vectors $\ArmV{i} \in \R^d$.
The \ArmV{i} are (adversarially) fixed, but unknown to the agents
or the principal.
Whenever arm $i$ is pulled, its current utility-relevant features are
determined as $\ArmV{i} + \NoiseV$, where \NoiseV is a mean-zero \pfedit{independent} 
Gaussian%
\footnote{For simplicity of notation, we assume that the variance
  $\sigma^2$ is uniform across time steps. This is not material for
  the analysis.}
noise vector $\NoiseV \sim \Normal{\vc{0}}{\sigma^2 I_{d}}$.
\dkcomment{Clarify if we can handle more general noise.}
Here, $I_d$ denotes the $d \times d$ identity matrix.

At each time $t$, a new user (or \emph{agent}) arrives,
whose feature vector (which we also call his%
\footnote{We use male pronouns to refer to users and female pronouns
  to refer to the principal.}
\emph{type}) $\AgentV{t} \in \R^d$ is drawn from a known distribution
\AgentDist.
Depending on context, we will identify agents with their arrival time
$t$ or their type \AgentV{t}.
When agent $t$ pulls arm $\Pull{t} := i$,
he and all future agents observe a vector
$\ObsV{t} = \ArmV{i} + \NoiseV[t]$ for arm $i$,
and his reward is $\AgentV{t} \cdot \ObsV{t}$,
i.e., agents have linear preferences.

@@

Since each user only pulls an arm once, users are \emph{myopic}:
in the absence of incentives, user $t$ will pull an arm from
$\argmax_i \AgentV{t} \cdot \ArmEV{t}{i}$.
To incentivize users to explore more, the principal can offer
\emph{payments} $\Pay{t}{i}$ to user $t$ for pulling arm $i$.
Then, user $t$ will pull an\footnote{We assume that ties are broken in
  favor of an arm with largest payment \Pay{t}{i}; this assumption is
  only for notational convenience, and can of course be avoided by
  raising payments infinitesimally.
  \pfcomment{In the finite preference setting this is clear, but it's a little bit delicate when there are continuum preferences, since regardless of the payment we offer there may always be support within our preference distribution for a $\theta$ that causes a tie.  In this continuum setting it should instead be possible to perturb infinitessimally so that we avoid ties with probability 1.}  
  } arm $i$ maximizing
$\argmax_i (\Pay{t}{i} + \AgentV{t} \cdot \ArmEV{t}{i})$.
The principal cannot observe \AgentV{t},
and only knows the distribution \AgentDist from which it is drawn.
Her goal is to achieve a good tradeoff between the cumulative
\emph{regret} experienced by all users up to time $T$,
and the total \emph{payment} she makes to the users.

@@

To support the formulation of our results and the analysis,
we define the following additional notation.
We let
$\Best{\AgV} \in \argmax_i \AgV \cdot \ArmV{i}$
and
$ \Second{\AgV} \in \argmax_{i \neq \Best{\AgV}} \AgV \cdot \ArmV{i}$
denote the (indices of) the best and second-best arms for an agent
with attribute vector \AgV;
\dkdelete{breaking ties uniformly at random}.
\dkcomment{What would it mean to break ties at random in a
  definition?}
\pfcomment{Perhaps we should say instead ``breaking ties arbitrarily'' if our results don't depend on how we break ties.}

\dkcomment{Do we need this definition here?}\pfcomment{I agree that we can move the definition of phase to where we define our algorithm.}
We call time $t_{n}=\min_{t}\{\forall i, \NumPull{t}{i} \geq n\}$ the
\emph{starting point of the $n^{th}$ phase}.
We call the set of times $[t_{n}, t_{n+1})$ the
\emph{$n^{th}$ round}.

@@

Let $\FirstTwo{i}{i'} = \Set{\AgV}{\Best{\AgV} = i, \Second{\AgV} = i'}$
be the set of agent attribute vectors whose best arm is $i$ and
second-best arm is $i'$.
Let $F_{i,i'}$ be the marginal cumulative density function
(or cumulative mass function if $\AgentDist(\cdot)$ is a discrete distribution)
\pfcomment{Maybe this should just be the conditional cumulative distribution function, 
$F_{i,i'}(z) = \Prob[\AgentDist]{(\ArmV{i}-\ArmV{i'}) \cdot \AgV \le z \mid \AgV \in \Omega_{i,i^{'}}}$?}
of $(\ArmV{i}-\ArmV{i'}) \cdot \AgV$,
conditioned on $\AgV \in \Omega_{i,i^{'}}$.
In words, $F_{i,i'}$ is the distribution of the \emph{strength} of the
preference of a random agent for arm $i$ over arm $i'$, given that
$i$ and $i'$ are the agent's first and second choices.
\pfcomment{We should say something about what $F_{i,i'}$ is when $\Prob[\AgentDist]{\AgV \in \Omega_{i,i^{'}}}=0$.  We know that arm $i$ is someone's best arm, but it doesn't have to be possible for $i'$ to be someone's second best arm when $i$ is best.  Maybe we can just set $F_{i,i'}$ to be $0$ in that case.}
